Notes on modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-06-28 docs/mvfits_paper/mvf.tex
adding plots for toy problem and new python issues

In that setting, the \qnm{} frequencies impact the morphology of each $h\LM$ in not only \rd{}, but also merger and late inspiral.

@@

The study of smooth scalar functions (e.g. $\vecf$) often centers about the Taylor series expansion.

@@

>>>>

In that setting, it is demonstrated that \qnm{} frequencies correlate with the morphology of each $h\LM$ in not only \rd{}, but also merger and late inspiral, as is implied by the causal connectedness of pre and post merger.

@@

The study of smooth scalar functions (e.g. $f(\vec{x})$) often centers about the Taylor series expansion.

@@

% Plots of mixing coefficients
\begin{figure*}
  %
  \begin{tabular}{lcr}
    \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_3.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_4.pdf}
  \end{tabular}
  %
	\caption{ Percentage residual errors for spherical-spheroidal harmonic mixing coefficient models. }
  %
\end{figure*}
